Binning Strategies and Related Loss for Large Data

### 2015-03-31 Paper.Rnw
Add stripped plot to section 5.1 showing what happens when binwidth is not integer multiple of data resolution.

Consider the simulated uniform data, we have the fine version and the coarse version, which rounded to nearest even integer. Figure~\ref{fig:strippedplots} displays the binned scatterplots under several scenarios.

>>>>

Consider the simulated uniform data, we have the fine version and the coarse version, which rounded to nearest even integer. Figure~\ref{fig:UniformStripes} displays the binned scatterplots under several scenarios.

<<UniformStripes, echo=F,include=T,eval=T,fig.width=5, fig.height=5, out.width='.7\\linewidth', fig.pos='h',fig.align='center',tidy=F, cache=TRUE, fig.show='hold',fig.cap="Binned Scatterplots of Uniform Data with 5X5 Bins">>= 
### Binned Scatterplots for Uniform Data to Show stripes
# create binned data for standard and random with binwidth 5
binoutfine <- RectBin2d(datlist[[1]]$x,datlist[[1]]$y,0,0,5,5,type="standard")
binoutcoarse <- RectBin2d(datlist[[1]]$roundx,datlist[[1]]$roundy,0,0,5,5,type="standard")
binoutfineRand <- RectBin2d(datlist[[1]]$x,datlist[[1]]$y,0,0,5,5,type="random")
binoutcoarseRand <- RectBin2d(datlist[[1]]$roundx,datlist[[1]]$roundy,0,0,5,5,type="random")

allbindat <- rbind(binoutfine[[1]],binoutcoarse[[1]],
                   binoutfineRand[[1]],binoutcoarseRand[[1]])
allbindat$SimDataType <- factor(rep(c("Fine","Coarse","Fine","Coarse"), 
                             each=nrow(binoutfine[[1]])),
                             levels=c("Fine","Coarse"))
allbindat$BinningType <- factor(rep(c("Standard","Random"),
                             each=2*nrow(binoutfine[[1]])),
                             levels=c("Standard","Random"))

qplot(binxs, binys, geom="tile", fill=binfreq, data=allbindat) +
  facet_grid(BinningType ~ SimDataType)+
  ggtitle(" ") +  
  scale_fill_gradient(low="#56B1F7", high="#132B43",
                      limits=c(0, 450),name="Bin Count") + 
  theme_bw() + theme(legend.position="bottom",aspect.ratio=1) +
  xlab("X") + ylab("Y")
@
